Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 delegations.tex
Mention the possibility to achieve security
add TODO

\begin{definition}
	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here.
\end{definition}

@@

>>>>

\begin{definition}
	A quantum delegation protocol is \emph{secure} if a malicious prover cannot learn the input or the output of the computation. In particular, security notions such as \emph{CPA} can be applied here. (TODO Just define CPA right away since there are no other security notions around here)
\end{definition}

@@

\subsection{Our contributions}

We start by constructing a verifiable long output scheme. Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security. TODO Does it actually work though? There are multiple steps in the scheme... We encrypting each step separately or what?
